INTELLIGENT SYSTEMS

### 2021-04-17 papers/paper_8.tex
finish 8.4.3

>>>>

\subsubsection{Experimental Setup}
The experiments were conducted on four different types of datasets: OTB-2013 
\cite{0893551142}, OTB-100 \cite{0893551143}, VOT-2015 \cite{0893551144} and VOT-2016 \cite{0893551140}. The first two contain 
a total of 150 bounding-box annotated videos and two metrics, precision 
plots and success plots were used to assess the quality of the tracing. The 
first metric reaches a high value when the distance between the bounding-box 
(ground-truth) centers and the predicted one are less than a certain threshold, 
while the second metric takes into account the overlap of the two components, 
which is calculated with \emph{IoU} index. The last two datasets contain 
a total of 100 videos and the metrics to evaluate the tracking are accuracy, 
robustness and the expected average overlap (\emph{EAO}). To be considered good, 
a tracker must achieve high accuracy and a high AEO score, while it must 
achieve a low robustness score.
